### 2021-04-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{myexample}
Shown in Figure~\ref{fig:design:example2}, we have the following observation from $k_1$ to $k_8$, then we count the distribution of  the observation. The process is like traversing a binary tree and increase the counter of the child node. According to Definition~\ref{chapter5:def}, the amount of the leakage is

@@

Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \tool{} and \ctool{}. First, as the result indicates, the leakage sites that leak more information (> 5.0 bits) are all fixed in OpenSSL 1.1.1. The result indicates that \ctool{} can help developers identify side-channel leakages and pick the severe from them automatically. As expected, we find most of the leakages are from the big number calculations. OpenSSL has a side-channel mitigated big number implementation. As long as big numbers are derived from secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}. However, the flag is off by default. We find developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}. Second, for those leakage sites that are not fixed by the developers, both \tool{} and \ctool{} report that they leak less amount of information. For example, function \textsf{BN\_mod\_exp\_mont\_consttime} check if the modulus is odd. However, it is not a side-channel leakage vulnerability. Both tools report the leakage site can leak one bit of information. Third, even \tool{} reports some leakage sites leak little information, \ctool{} can report the vulnerability is severe. \tool{} quantifies the amount of leaked information for one execution. So it is possible that some leakage sites leak little information for one input but leak more information for a different input. We run the chi-squared test to determine if any two leaked functions have independent leakages.

@@

\begin{figure}
  \centering
  \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
int foo(uint8_t secret){
  uint8_t index = 0, t;
  index = (index+secret)%128; // The index contains secrets
  ...
  if(index == 0){             // Secret-dependent flows
    bar(r, x, n)              // The observation
  }
  ...
}
\end{lstlisting}
  \caption{A code fragment}
  \label{fig:limitation}
\end{figure}

>>>>

\begin{myexample}
Shown in Figure~\ref{fig:design:example2}, we have the following observation from $k_1$ to $k_8$, then we count the distribution of  the observation. The process is like traversing a binary tree and increase the counter of the child node. According to Definition~\ref{chapter5:def}, the amount of the leakage is $1.4$ $\mathit{bits}$.

@@

Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the leaked function and the amount of leakage reported by \tool{} and \ctool{}. First, as the result indicates, the leakage sites that leak more information (> 5.0 bits) are all fixed in OpenSSL 1.1.1. The result indicates that \ctool{} can help developers identify side-channel leakages and pick the severe from them automatically. As expected, we find most of the leakages are from the big number calculations. OpenSSL has a side-channel mitigated big number implementation. As long as big numbers are derived from secret data, the big number should be enabled with the flag \textsf{BN\_FLG\_CONSTTIME}. However, the flag is off by default. We find developers forget to propagate the flag in the caller, which results in the vulnerabilities in \textsf{BN\_div} and \textsf{int\_bn\_mod\_inverse}. Second, for those leakage sites that are not fixed by the developers, both \tool{} and \ctool{} report that they leak less amount of information. For example, function \textsf{BN\_mod\_exp\_mont\_consttime} check if the modulus is odd. However, it is not a side-channel leakage vulnerability. Both tools report the leakage site can leak one bit of information. Third, even \tool{} reports some leakage sites leak little information, \ctool{} can report the vulnerability is severe. \tool{} quantifies the amount of leaked information for one execution. So it is possible that some leakage sites leak little information for one input but leak more information for a different input. We run the chi-squared test to determine if any two leaked functions have independent leakages. However, we can not conclude any two leakages are independent under the chi-squared test. We think it is due to the avalanche effect in cryptography.

@@

\begin{figure}
  \centering
  \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
int foo(uint8_t secret){
  uint8_t index = 0, t;
  index = (index+secret)%128; // The index contains secrets
  ...
  if(index == 0){             // Secret-dependent flows
    bar(r, x, n)              // The observation
  }
  ...
}
\end{lstlisting}
  \caption{The reported leaked functions are not the root cause of the vulernability}
  \label{fig:limitation}
\end{figure}

### 2021-04-16 SupplementaryMaterial/Acknowledgments.tex
Updates from Overleaf

% Place acknowledgments below.
First of all, I would like to thank my advisor Dr. Dinghao Wu for the continuous support of my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program. I also thank Dinghao for inviting me to Switzerland on his sabbatical. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. The knowledge and skills I learned from him will also help me make progress in my future career.

Beside my advisor, I would like to thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin V. Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.

I would also like to thank Dr. Kang Li, Mr. Zhaofeng Chen, Dr. Mingshen Sun, Dr. Greg Zaverucha, Dr. Kevin Kane, and Dr. Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research Lab.  I also thank my friends and collaborators at Penn State University and EPFL.

>>>>

% Place acknowledgments below.
I am tremendously fortunate to have been advised by Dr. Dinghao Wu.  I thank Dinghao for inviting me to EPFL on his sabbatical. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. The knowledge and skills I learned from him will also help me make progress in my future career. I also think him for treating me as an independent researcher since the forth year of my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program.

Beside my advisor, I also thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin Hanrahan, and Dr. James Larus for their time, reviewing my dissertation. Without the strong encouragement from Dr. Peng Liu's former students in 2015, I would not have applied for Penn State.

Pursuing a Ph.D. can be extremely stressful, but summer internships are always the relaxing and productive moments during my study. I would also like to thank Dr. Kang Li, Mr. Zhaofeng Chen, Dr. Mingshen Sun, Dr. Greg Zaverucha, Dr. Kevin Kane, and Dr. Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research.  I also thank my friends and collaborators at Penn State University and EPFL.
